IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/real.tex
nits

Luckly, this issue is not unique to our work---browser layout engines
also rely on isolating code of different origins (e.g., according to the
same-origin policy).
%
Since creating an OS thread for each iframe is expensive, both
the V8 and SpiderMonkey JavaScript engines provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
(We will use these terms interchangably.)
%
Each context is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, we adopt contexts to implement our notion of tasks.

>>>>

Luckly, this issue is not unique to our work---browser layout engines
also rely on isolating code executing in separate iframes (e.g., according to the
same-origin policy).
%
Since creating an OS thread for each iframe is expensive, both
the V8 and SpiderMonkey JavaScript engines provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
(We will use these terms interchangably.)
%
Each context is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, we adopt contexts to implement our notion of tasks.
